---
title: "The First Real Game"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = TRUE,
  fig.width=8,
  fig.height=8
)
```

## Intro

This just shows a brief example of how you can start a game and trigger turns to progress.

```{r, include=FALSE}
devtools::load_all()
if (fs::dir_exists(file.path(GAME_ROOT_DIR, "anno_duo"))) fs::dir_delete(file.path(GAME_ROOT_DIR, "anno_duo"))
```
```{r}
library(MundusCentrum)
```

### Setup the game

```{r}
game <- new_game(
  name = "Anno Duo",
  players = list(
    list(
      name = "Big Grizz",
      team = "Dark Angels",
      units = system.file("extdata", "unit-templates", "big_grizz.csv", package = "MundusCentrum")
    ),
    list(
      name = "Eric",
      team = "Necrons",
      units = system.file("extdata", "unit-templates", "eric.csv", package = "MundusCentrum")
    ),
    list(
      name = "Chris",
      team = "Tyranids",
      units = system.file("extdata", "unit-templates", "chris.csv", package = "MundusCentrum")
    )
  ),
  points = 3000
)
str(game)
```

### see the starting point
This is the state of the game at the beginning

```{r}
res <- reconcile_player_orders(game)
print(draw_map(res))
knitr::kable(res)
```

## Turn play

Get a list of unit ID's to easily make the `modify_unit()` calls below.

```{r}
moby_units <- read_player_map(game, "big_grizz") %>% pull(unit_name)
eric_units <- read_player_map(game, "eric") %>% pull(unit_name)
chris_units <- read_player_map(game, "chris") %>% pull(unit_name)
```

# TURN 1
Players change their maps (making orders)

```{r}
modify_unit(game, "big_grizz", moby_units[1],   "move",  "C2")
modify_unit(game, "big_grizz", moby_units[c(2, 7, 17, 18)],   "control",  "D4")
modify_unit(game, "big_grizz", moby_units[c(3, 5:6, 13, 22)],   "soar",  "H2") # transport
modify_unit(game, "big_grizz", moby_units[c(8, 23)],   "move",  "C5") # transport
modify_unit(game, "big_grizz", moby_units[9],   "move",  "F5")
modify_unit(game, "big_grizz", moby_units[c(10:12, 16)],   "move",  "D1")
modify_unit(game, "big_grizz", moby_units[c(14:15, 19:21)],   "move",  "F5")

modify_unit(game, "eric",      eric_units[c(1:6, 13:14, 8:11)],   "move",  "E7")
modify_unit(game, "eric",      eric_units[7],     "control","G7")
modify_unit(game, "eric",      eric_units[12],     "move","E5")
modify_unit(game, "eric",      eric_units[15:18],   "soar","I4") # transport
modify_unit(game, "eric",      eric_units[19],   "move","G6")
modify_unit(game, "eric",      eric_units[20],   "move","E6")
modify_unit(game, "eric",      eric_units[21],   "move","E4")
modify_unit(game, "eric",      eric_units[c(22:24, 26)],   "soar", c("G8","H3")) # transport
modify_unit(game, "eric",      eric_units[25],   "move","G8")
modify_unit(game, "eric",      eric_units[27],   "move","F4")
modify_unit(game, "eric",      eric_units[28],   "move","F8")

modify_unit(game, "chris",     chris_units[c(6, 13)],  "move","A2")
modify_unit(game, "chris",     chris_units[c(5, 7, 8, 12, 23)],  "move","A3")
modify_unit(game, "chris",     chris_units[1],  "move","A4")
modify_unit(game, "chris",     chris_units[c(10, 14, 24)],  "move","A6")
modify_unit(game, "chris",     chris_units[c(3, 9, 17, 18, 22)],  "move","A7")
modify_unit(game, "chris",     chris_units[2],  "move","A8")
modify_unit(game, "chris",     chris_units[19],  "move","B10")
modify_unit(game, "chris",     chris_units[21],  "move","B11")
modify_unit(game, "chris",     chris_units[c(4, 15)],  "move","B7")
modify_unit(game, "chris",     chris_units[20],  "move","E1")
modify_unit(game, "chris",     chris_units[c(11, 16, 25)],  "control","A5")

```

Attempt to reconcile moves.

```{r}
res <- reconcile_player_orders(game)
print(draw_map(res))
knitr::kable(res)
```

```{r}
#print(draw_map(res))
print(draw_map(res, "big_grizz"))
print(draw_map(res, "chris"))
print(draw_map(res, "eric"))

```

### Resolve conflicts

```{r}
# modify_unit(game, "big_grizz", "A2",   "control","A3")
# res <- reconcile_player_orders(game)
# print(draw_map(res, "big_grizz"))
```

# TURN 2
Players change their maps (making orders)

```{r}
modify_unit(game, "big_grizz", moby_units[1],   "move",  "B4")
modify_unit(game, "big_grizz", moby_units[7],   "move",  "D2")
modify_unit(game, "big_grizz", moby_units[6],   "move",  "H5")
modify_unit(game, "big_grizz", moby_units[c(3, 5, 13, 22)],   "control",  "H2")
modify_unit(game, "big_grizz", moby_units[c(8, 23)],   "control",  "C5")
modify_unit(game, "big_grizz", moby_units[9],   "control",  "F5")
modify_unit(game, "big_grizz", moby_units[c(10:12, 16)],   "move",  "B4")
modify_unit(game, "big_grizz", moby_units[c(14:15, 19:21)],   "move",  "C5")

modify_unit(game, "eric",      eric_units[c(1:6, 13:14, 8:11)],   "move",  "E5")
modify_unit(game, "eric",      eric_units[7],     "move","E7")
modify_unit(game, "eric",      eric_units[12],     "move","F2")
modify_unit(game, "eric",      eric_units[c(15,18)],     "control","I4")
modify_unit(game, "eric",      eric_units[16:17],   "move","I5")
modify_unit(game, "eric",      eric_units[19],   "control","G6")
modify_unit(game, "eric",      eric_units[20],   "move","E3")
modify_unit(game, "eric",      eric_units[21],   "move","A8")
modify_unit(game, "eric",      eric_units[c(22:24, 26)],   "move","H2")
modify_unit(game, "eric",      eric_units[25],   "control","G8")
modify_unit(game, "eric",      eric_units[27],   "move","F5")
modify_unit(game, "eric",      eric_units[28],   "move","H3")

modify_unit(game, "chris",     chris_units[c(6)],  "move","A4")
modify_unit(game, "chris",     chris_units[c(13)],  "control","A2")
modify_unit(game, "chris",     chris_units[c(5, 12, 23)],  "move","B2")
modify_unit(game, "chris",     chris_units[c(7, 8)],  "control","A3")
modify_unit(game, "chris",     chris_units[1],  "move","A8")
modify_unit(game, "chris",     chris_units[c(14)],  "control","A6")
modify_unit(game, "chris",     chris_units[c(10, 24)],  "move","A8")
modify_unit(game, "chris",     chris_units[c(3,17, 18, 22)],  "move","B9")
modify_unit(game, "chris",     chris_units[c(9)],  "control","A7")
modify_unit(game, "chris",     chris_units[2],  "move","E1")
modify_unit(game, "chris",     chris_units[19],  "move","E1")
modify_unit(game, "chris",     chris_units[21],  "move","B6")
modify_unit(game, "chris",     chris_units[c(4)],  "move","B8")
modify_unit(game, "chris",     chris_units[c(15)],  "move","B9")
modify_unit(game, "chris",     chris_units[20],  "move","E2")
modify_unit(game, "chris",     chris_units[11],  "move","B7")
modify_unit(game, "chris",     chris_units[c(16, 25)],  "control","A5")

```

Attempt to reconcile moves.

```{r}
res <- reconcile_player_orders(game)
print(draw_map(res))
knitr::kable(add_keywords(res))
```



### Resolve conflicts

```{r}
# retreats
modify_unit(game, "eric", "F5",   "move","F8")
kill_unit(game, "eric", eric_units[21])
modify_unit(game, "eric", "H2",   "move","H3")

res <- reconcile_player_orders(game)
knitr::kable(res)
print(draw_map(res))
```


```{r}
print(draw_map(res, "big_grizz"))
print(draw_map(res, "chris"))
print(draw_map(res, "eric"))

```
