---
title: "Sample Game - Maps Only"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = TRUE,
  fig.width=8,
  fig.height=8
)
```

## Intro

This is just the same thing as the ["Sample Game" vignette](https://seth127.github.io/MundusCentrum/sample-game), but with only the global maps (and player moves) shown. The idea is be able to more easily follow the flow of the game.

```{r, include=FALSE}
devtools::load_all()
if (fs::dir_exists(file.path(GAME_ROOT_DIR, "anno_uno"))) fs::dir_delete(file.path(GAME_ROOT_DIR, "anno_uno"))
```
```{r}
library(MundusCentrum)
```

### Setup the game

```{r}
game <- new_game(
  name = "Anno Uno",
  players = list(
    list(
      name = "Big Grizz",
      team = "Space Marines",
      units = system.file("extdata", "unit-templates", "big_grizz.csv", package = "MundusCentrum")
    ),
    list(
      name = "Eric",
      team = "Space Orcs",
      units = system.file("extdata", "unit-templates", "eric.csv", package = "MundusCentrum")
    ),
    list(
      name = "Chris",
      team = "Tyrannids",
      units = system.file("extdata", "unit-templates", "chris.csv", package = "MundusCentrum")
    )
  ),
  points = 2000
)
```

### see the starting point
This is the state of the game at the beginning

```{r}
res <- reconcile_player_orders(game)
print(draw_map(res))
```

## Turn play

Get a list of unit ID's to easily make the `modify_unit()` calls below.

```{r}
moby_units <- read_player_map(game, "big_grizz") %>% pull(unit_name)
eric_units <- read_player_map(game, "eric") %>% pull(unit_name)
chris_units <- read_player_map(game, "chris") %>% pull(unit_name)
```

# TURN 1
Players change their maps (making orders)

```{r}
modify_unit(game, "big_grizz", moby_units[1],     "control","B10")
modify_unit(game, "big_grizz", moby_units[c(2:8, 14:18, 22, 23)], "move", "E2")
modify_unit(game, "big_grizz", moby_units[9],     "control","B11")
modify_unit(game, "big_grizz", moby_units[10:13], "move","E1")
modify_unit(game, "big_grizz", moby_units[19:20], "move","B6")
modify_unit(game, "big_grizz", moby_units[21],    "move","B8")
modify_unit(game, "eric",      eric_units[1:9],   "move",  "C1")
modify_unit(game, "eric",      eric_units[10:17], "move","F7")
modify_unit(game, "eric",      eric_units[18:24], "control","C3")
modify_unit(game, "eric",      eric_units[25:28], "control","C4")
modify_unit(game, "chris",     chris_units[1:5],  "control","F1")
modify_unit(game, "chris",     chris_units[6:9],  "control","F2")
modify_unit(game, "chris",     chris_units[10:11],"move",  "F3")
modify_unit(game, "chris",     chris_units[12],"move",  "E5")
modify_unit(game, "chris",     chris_units[13],"move",  "F4")

res <- reconcile_player_orders(game)
print(draw_map(res))
```

# TURN 2

```{r}
modify_unit(game, "big_grizz", "E2",   "attack",  "F1")
modify_unit(game, "big_grizz", "B6",   "control", "B6")
modify_unit(game, "big_grizz", "B11",  "attack",  "E3")
modify_unit(game, "big_grizz", "B8",   "attack",  "B2")
modify_unit(game, "big_grizz", "E1",   "attack",  "B2")
modify_unit(game, "chris",     "E5",   "move",    "E5") # 1 units
modify_unit(game, "chris",     "F1",   "control", "F1") # 5 units
modify_unit(game, "chris",     "F2",   "control", "F2") # 4 units
modify_unit(game, "chris",     "F3",   "move",    "F4") # 2 units
modify_unit(game, "chris",     "F4",   "control", "F4") # 1 units
modify_unit(game, "eric",      "F7",   "attack",  "F4") # 8 units
modify_unit(game, "eric",      "C1",   "move",    "B4") # 9 units

res <- reconcile_player_orders(game)
print(draw_map(res, "CONFLICT!"))
```

### Fights are resolved

```{r}
modify_unit(game, "eric",      "F4",  "retreat", "F7")
modify_unit(game, "chris",     "F1",  "retreat", "F2")

res <- reconcile_player_orders(game)
print(draw_map(res))
```

# TURN 3

```{r}
modify_unit(game, "big_grizz",   "B2",   "move",    "B1") # 5 units
modify_unit(game, "big_grizz",   "B6",   "move",    "C1") # 2 units
modify_unit(game, "big_grizz",   "E3",   "move",    "E4") # 1 units
modify_unit(game, "big_grizz",   "F1",   "control", "F1") # 14 units
modify_unit(game, "chris",       "E5",   "move",    "E7") # 1 units
modify_unit(game, "chris",       "F2",   "control", "F2") # 9 units
modify_unit(game, "chris",       "F4",   "control", "F4") # 3 units
modify_unit(game, "eric",        "B4",   "move",    "B1") # 9 units
modify_unit(game, "eric",        "C3",   "control", "C3") # 7 units
modify_unit(game, "eric",        "F7",   "control", "F7") # 8 units

res <- reconcile_player_orders(game)
print(draw_map(res, "CONFLICT!"))
```

### Encounter battles

```{r}
modify_unit(game, "big_grizz",  "B1", "retreat", "B2") # 5 units
res <- reconcile_player_orders(game)
```
# TURN 4

```{r}
modify_unit(game, "big_grizz",   "B2",   "control", "B2") # 5 units
modify_unit(game, "big_grizz",   "C1",   "move",    "B4") # 2 units
modify_unit(game, "big_grizz",   "E4",   "move",    "E6") # 1 units
modify_unit(game, "big_grizz",   "F1",   "control", "F1") # 14 units
modify_unit(game, "chris",       "E7",   "move",    "F8") # 1 units
modify_unit(game, "chris",       "F2",   "attack",  "F1") # 9 units
modify_unit(game, "chris",       "F4",   "attack",  "F7") # 3 units
modify_unit(game, "eric",        "B1",   "attack",  "B2") # 9 units
modify_unit(game, "eric",        "F7",   "control", "F7") # 8 units

res <- reconcile_player_orders(game)
print(draw_map(res, "CONFLICT!"))
```

### Fights are resolved

```{r}
modify_unit(game, "big_grizz",   "F1",   "retreat", "E2") # 14 units
modify_unit(game, "eric",        "B2",   "retreat", "B1") # 9 units
modify_unit(game, "eric",        "F7",   "retreat", "F8") # 8 units

res <- reconcile_player_orders(game)
print(draw_map(res, "CONFLICT!"))
```

### Retreats

```{r}
modify_unit(game, "eric",  "F8", "retreat", "F5") # 5 units
res <- reconcile_player_orders(game)
```

# TURN 5

```{r}
print(draw_map(res))
knitr::kable(add_keywords(res))
```

