---
title: "Sample Game"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = TRUE,
  fig.width=8,
  fig.height=8
)
```

## Intro

This just shows a brief example of how you can start a game and trigger turns to progress.

```{r, include=FALSE}
devtools::load_all()
if (fs::dir_exists(file.path(GAME_ROOT_DIR, "anno_uno"))) fs::dir_delete(file.path(GAME_ROOT_DIR, "anno_uno"))
```
```{r}
library(MundusCentrum)
```

### Setup the game

```{r}
game <- new_game(
  name = "Anno Uno",
  players = list(
    list(
      name = "Big Grizz",
      team = "Space Marines",
      units = system.file("extdata", "unit-templates", "big_grizz.csv", package = "MundusCentrum")
    ),
    list(
      name = "Eric",
      team = "Space Orcs",
      units = system.file("extdata", "unit-templates", "eric.csv", package = "MundusCentrum")
    ),
    list(
      name = "Chris",
      team = "Tyrannids",
      units = system.file("extdata", "unit-templates", "chris.csv", package = "MundusCentrum")
    )
  ),
  points = 2000
)
```

### see the starting point
This is the state of the game at the beginning

```{r}
res <- reconcile_player_orders(game)
print(draw_map(res))
knitr::kable(add_keywords(res))
```

## Turn play

Get a list of unit ID's to easily make the `modify_unit()` calls below.

```{r}
moby_units <- read_player_map(game, "big_grizz") %>% pull(unit_name)
eric_units <- read_player_map(game, "eric") %>% pull(unit_name)
chris_units <- read_player_map(game, "chris") %>% pull(unit_name)
```

# TURN 1
Players change their maps (making orders)

```{r}
modify_unit(game, "big_grizz", moby_units[1],     "control","B10")
modify_unit(game, "big_grizz", moby_units[c(2:8, 14:18, 22, 23)], "move", "E2")
modify_unit(game, "big_grizz", moby_units[9],     "control","B11")
modify_unit(game, "big_grizz", moby_units[10:13], "move","E1")
modify_unit(game, "big_grizz", moby_units[19:20], "move","B6")
modify_unit(game, "big_grizz", moby_units[21],    "move","B8")
modify_unit(game, "eric",      eric_units[1:9],   "move",  "C1")
modify_unit(game, "eric",      eric_units[10:17], "move","F7")
modify_unit(game, "eric",      eric_units[18:24], "control","C3")
modify_unit(game, "eric",      eric_units[25:28], "control","C4")
modify_unit(game, "chris",     chris_units[1:5],  "control","F1")
modify_unit(game, "chris",     chris_units[6:9],  "control","F2")
modify_unit(game, "chris",     chris_units[10:11],"move",  "F3")
modify_unit(game, "chris",     chris_units[12],"move",  "E5")
modify_unit(game, "chris",     chris_units[13],"move",  "F4")
```

Reconcile moves.

```{r}
res <- reconcile_player_orders(game)
print(draw_map(res))
knitr::kable(add_keywords(res))
```

Take a look at what individual players can see. Here's Chris' map:

```{r}
draw_map(res, "chris")
```

We're good! Move on to the next turn. (Battle awaits!)


# TURN 2
Players change their maps (making orders)

```{r}
# uncomment to print the calls you would make to move all units
#modify_unit_calls(res)
```


```{r}
modify_unit(game, "big_grizz", "E2",   "attack",  "F1")
modify_unit(game, "big_grizz", "B6",   "control", "B6")
modify_unit(game, "big_grizz", "B11",  "attack",  "E3")
modify_unit(game, "big_grizz", "B8",   "attack",  "B2")
modify_unit(game, "big_grizz", "E1",   "attack",  "B2")
modify_unit(game, "chris",     "E5",   "move",    "E5") # 1 units
modify_unit(game, "chris",     "F1",   "control", "F1") # 5 units
modify_unit(game, "chris",     "F2",   "control", "F2") # 4 units
modify_unit(game, "chris",     "F3",   "move",    "F4") # 2 units
modify_unit(game, "chris",     "F4",   "control", "F4") # 1 units
modify_unit(game, "eric",      "F7",   "attack",  "F4") # 8 units
modify_unit(game, "eric",      "C1",   "move",    "B4") # 9 units
```

Attempt to reconcile moves.

```{r}
res <- reconcile_player_orders(game)
print(draw_map(res, "CONFLICT!"))
knitr::kable(add_keywords(res))
```

### Fights are resolved
This is where the players would resolved fights however they see fit (e.g. Warhammer, chessboxing, what-have-you)

Then they adjust their maps accordingly for the outcome of the conflicts.

```{r}
modify_unit(game, "eric",      "F4",  "retreat", "F7")
modify_unit(game, "chris",     "F1",  "retreat", "F2")
```

Now we reconcile again.

```{r}
res <- reconcile_player_orders(game)
print(draw_map(res))
knitr::kable(add_keywords(res))
```

We're good. On to turn 3.

### NOTE: Crossing Paths

Notice that in this turn Chris and Eric sit across from each other in `F2` and `C3`, their respective starting spots. At this point they should fight, but the mechanic isn't clear. If `C4 attacks F2` and `F2 attacks C4` then, as it's currently coded, they would pass in the night. This is not right. 

Unfortunately, this will be more complicated with longer moves, but we probably still need to trace the paths because, when paths cross, swords must cross.

# TURN 3
Players change their maps (making orders)


```{r}
modify_unit(game, "big_grizz",   "B2",   "move",    "B1") # 5 units
modify_unit(game, "big_grizz",   "B6",   "move",    "C1") # 2 units
modify_unit(game, "big_grizz",   "E3",   "move",    "E4") # 1 units
modify_unit(game, "big_grizz",   "F1",   "control", "F1") # 14 units
modify_unit(game, "chris",       "E5",   "move",    "E7") # 1 units
modify_unit(game, "chris",       "F2",   "control", "F2") # 9 units
modify_unit(game, "chris",       "F4",   "control", "F4") # 3 units
modify_unit(game, "eric",        "B4",   "move",    "B1") # 9 units
modify_unit(game, "eric",        "C3",   "control", "C3") # 7 units
modify_unit(game, "eric",        "F7",   "control", "F7") # 8 units

```

Attempt to reconcile moves.

```{r}
res <- reconcile_player_orders(game)
print(draw_map(res, "CONFLICT!"))
knitr::kable(add_keywords(res))
```

### Encounter battles

Another fight, this time in `B1`, but neither force was attacking or controlling. They just ran into each other. Does this play differently? Bonuses or lack thereof?

```{r}
modify_unit(game, "big_grizz",  "B1", "retreat", "B2") # 5 units
res <- reconcile_player_orders(game)
```


### Controlling? Healing?

I have Chris here holding to control in both `F2` (instead of attacking `F1`) and `F4` (instead of pursuing Eric into `F7`), and Eric holding `C3` and `F7`. I'm thinking maybe there is some benefit to resting like this? Getting reinforcements? Heailing?

(Mostly I just didn't want to process too many battles this turn)

### Vision

Sidenote: notice how everyone's vision changes... 

**Grizz**
```{r}
draw_map(res, "big_grizz")
```

**Chris**
```{r}
draw_map(res, "chris")
```

**Eric**
```{r}
draw_map(res, "eric")
```

# TURN 4
Players change their maps (making orders). Renew the attack.

```{r}
modify_unit(game, "big_grizz",   "B2",   "control", "B2") # 5 units
modify_unit(game, "big_grizz",   "C1",   "move",    "B4") # 2 units
modify_unit(game, "big_grizz",   "E4",   "move",    "E6") # 1 units
modify_unit(game, "big_grizz",   "F1",   "control", "F1") # 14 units
modify_unit(game, "chris",       "E7",   "move",    "F8") # 1 units
modify_unit(game, "chris",       "F2",   "attack",  "F1") # 9 units
modify_unit(game, "chris",       "F4",   "attack",  "F7") # 3 units
modify_unit(game, "eric",        "B1",   "attack",  "B2") # 9 units
modify_unit(game, "eric",        "F7",   "control", "F7") # 8 units
```

Attempt to reconcile moves.

```{r}
res <- reconcile_player_orders(game)
print(draw_map(res, "CONFLICT!"))
knitr::kable(add_keywords(res))
```

### Fights are resolved
We fight. Adjust maps accordingly for the outcome of the conflicts.

```{r}
modify_unit(game, "big_grizz",   "F1",   "retreat", "E2") # 14 units
modify_unit(game, "eric",        "B2",   "retreat", "B1") # 9 units
modify_unit(game, "eric",        "F7",   "retreat", "F8") # 8 units
```

Now we reconcile again.

```{r}
res <- reconcile_player_orders(game)
print(draw_map(res, "CONFLICT!"))
knitr::kable(add_keywords(res))
```

### Retreats

_Here's a good question: what happens here? A large army retreats into an area where a spy has been hiding. Do they fight? Do they take casualties?_

```{r}
modify_unit(game, "eric",  "F8", "retreat", "F5") # 5 units
res <- reconcile_player_orders(game)
```

Until we decide on that, I just made Eric retreat to `F5` instead. Another question: could he have retreated to `C5`? It borders `F7` where the battle started, but _not_ `F8` where the retreat conflict happened. Not sure on this one...

```{r}
# sidenote: I originally did this by accident but I saved myself with this warning
modify_unit(game, "big_grizz",  "F8", "retreat", "F5") # 5 units
```

# TURN 5
Here's how the map stands at the beginning of Turn 5...

```{r}
print(draw_map(res))
knitr::kable(add_keywords(res))
```

